---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r, echo = FALSE, warnings = FALSE}
#Packages
library(rgdal)    
library(ggplot2)   
library(maptools)
library(raster)
library(dplyr)

#Import Shapefiles
s <- shapefile("/Users/lorenzoflores/Desktop/Yale_Academic/Stat Projects/Congress/Province Shapefiles/Provinces.shp")
s <- s[order(s$PROVINCE),]
s$PROVINCE <- sapply(s$PROVINCE,toupper)
```

```{r, echo = FALSE, warnings = FALSE}
#Import Data
genderProvince <- read.csv("/Users/lorenzoflores/Desktop/Yale_Academic/Stat Projects/Congress/Province Shapefiles/genderProvince.csv")
polParty <- read.csv("/Users/lorenzoflores/Desktop/Yale_Academic/Stat Projects/Congress/Province Shapefiles/polPartyData.csv")
provParty <- read.csv("/Users/lorenzoflores/Desktop/Yale_Academic/Stat Projects/Congress/Province Shapefiles/provPartyData.csv")
```

```{r, echo = FALSE, warnings = FALSE}
#Gives data for cities in Manila
processMap <- function(data){
  dataProcess <- data[data$Province %in% setdiff(data$Province,s$PROVINCE),]
  dataProcess <- dataProcess[!(sapply(dataProcess$Province,toupper) %in% sapply(c("","Bacolod","Bacolod City","Baguio", "Baguio City","Cagayan de Oro","Cagayan de Oro City","Calamba","Cebu City","Cotabato","Cotabato (North)","Davao (Davao del Norte)","Davao City", "Davao Occidental","Dinagat Islands6","Iligan","Iligan City","Iloilo City","Kalinga-Apayao","Lapu-Lapu City","Samar (Western)","San Jose del Monte","San Jose del Monte City","Zamboanga City"), toupper)),]
  return (dataProcess)
}
```

```{r, echo = FALSE, warnings = FALSE}
genderProvince$Province <- sapply(as.character(genderProvince$Province),toupper)
genderProvince$Province.1 <- sapply(as.character(genderProvince$Province.1),toupper)
genderProvince$Female <- as.numeric(genderProvince$Female)
genderProvince$Male <- as.numeric(genderProvince$Male)
genderProvince$Unidentified <- as.numeric(genderProvince$Unidentified)


#Get Manila data and process
genderProvinceManila <- processMap(genderProvince)
genderProvince[nrow(genderProvince)+1,] <- c("METROPOLITAN MANILA",round(mean(genderProvinceManila$Female),2),round(mean(genderProvinceManila$Male),2),round(mean(genderProvinceManila$Unidentified),2),"METROPOLITAN MANILA")
genderProvince[nrow(genderProvince)+1,] <- c("SHARIFF KABUNSUAN",0,0,0,"SHARIFF KABUNSUAN")
genderProvince <- genderProvince[!(genderProvince$Province %in% setdiff(genderProvince$Province,s$PROVINCE)),]

#Append to shapefile
genderProvince <- genderProvince[order(genderProvince$Province),]
s$female <- genderProvince$Female
```

```{r, echo = FALSE, warnings = FALSE}
polParty <- polParty[,-1]
polParty$Province <- sapply(as.character(polParty$Province),toupper)
polParty$Name <- as.character(polParty$Name)
polParty$Years <- as.integer(polParty$Years)
polParty$Count <- as.integer(polParty$Count)

#Get Manila data and process
polPartyManila <- processMap(polParty)
maxIndex <- which(polPartyManila$Count == max(polPartyManila$Count))

polParty[nrow(polParty)+1,] <- c("METROPOLITAN MANILA",polPartyManila$Name[maxIndex],polPartyManila$Years[maxIndex],polPartyManila$Count[maxIndex])
polParty[nrow(polParty)+1,] <- c("SHARIFF KABUNSUAN",'',0,0)
polParty <- polParty[!(polParty$Province %in% setdiff(polParty$Province,s$PROVINCE)),]

#Append to shapefile
polParty <- polParty[order(polParty$Province),]
s$dynasty <- polParty$Count
```

```{r, echo = FALSE, warnings = FALSE}
provParty <- provParty[,-1]
provParty$Province <- sapply(as.character(provParty$Province),toupper)
provParty$Party <- as.character(provParty$Party)
provParty$Years <- as.integer(provParty$Years)
provParty$Count <- as.integer(provParty$Count)

#Get Manila data and process
provPartyManila <- processMap(provParty)
maxIndex <- which(provPartyManila$Count == max(provPartyManila$Count))

provParty[nrow(provParty)+1,] <- c("METROPOLITAN MANILA",provPartyManila$Party[maxIndex],0,provPartyManila$Count[maxIndex])
provParty[nrow(provParty)+1,] <- c("SHARIFF KABUNSUAN",'',0,0)
provParty <- provParty[!(provParty$Province %in% setdiff(provParty$Province,s$PROVINCE)),]

#Append to shapefile
provParty <- provParty[order(provParty$Province),]
s$party <- provParty$Party
```
#### Female Representation by Province
Note: The more red the province, the more male representatives, the more blue the province, the  more female representatives, white is balanced (50% male, 50% female)
```{r, echo = FALSE, warnings = FALSE}
s$female <- as.numeric(s$female)
s$dynasty <- as.numeric(s$dynasty)

library(RColorBrewer)
library(viridis)

map2color<-function(x,pal,limits=NULL){
    if(is.null(limits)) limits=range(x)
    pal[findInterval(x,seq(limits[1],limits[2],length.out=length(pal)+1), all.inside=TRUE)]
}

img <- function(obj, nam) {
  image(1:length(obj), 1, as.matrix(1:length(obj)), col=obj, 
        main = nam, ylab = "", xaxt = "n", yaxt = "n",  bty = "n")
}
rwb <- colorRampPalette(colors = c("red", "white", "blue"))

colorFemale <- map2color(s$female, rwb(100))
plot(s, col = colorFemale, main = "Percent Female Representation by Province")
```

#### Length of Family with Most Terms as Congress Person
Note: Yellow is least (1-2 congress terms), dark red is most (10-11 congress terms)
```{r, echo = FALSE, warnings = FALSE}
colorDynasty <- map2color(s$dynasty, brewer.pal(9, 'YlOrRd'))
plot(s, col = colorDynasty, main = "Length of Longest Political Dynasty Province")
```

#### Party Fielding Most Congress Representatives by Province
Legend of Parties:

* Yellow: Liberal

* Light Blue: Lakas

* Blue: LDP

* Green: NPC

* Red: Nacionalista

* Orange: Independent

* Gray: Other
```{r, echo = FALSE, warnings = FALSE}
s$partyColor <- rep(NA,length(s$party))
s$partyColor[which(s$party == "Liberal")] <- "Yellow"
s$partyColor[which(s$party == "Lakas")] <- "Light Blue"
s$partyColor[which(s$party == "LDP")] <- "Blue"
s$partyColor[which(s$party == "NPC")] <- "Green"
s$partyColor[which(s$party == "Nacionalista")] <- "Red"
s$partyColor[which(s$party == "Independent")] <- "Orange"
s$partyColor[which(is.na(s$partyColor))] <- "Gray"
s$partyColor
```

```{r, echo = FALSE, warnings = FALSE}
plot(s, col = s$partyColor, main = "Dominant Party by Province")
```